\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\name{Christina Pizzonia} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\href{tel: 16477406134}{647-740-6134} $ \modcdot $ \href{mailto:christina.pizzonia@mail.utoronto.ca}{Email} $ \modcdot $ \href{https://linkedin.com/christina-pizzonia}{LinkedIn} $ \modcdot $ \href{https://github.com/endothermiic}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Summer Research Student} \hfill May 2022 - Aug 2022\\
Passeport Lab \hfill \textit{Toronto, ON}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved X\% growth for XYZ using A, \href{https://drive.google.com/file/d/1tVPh5Zt4zLT8spiLfzJ4vu0XZSuMfOfu/view}{extraction methods}B, and C skills.
     \item Led XYZ which led to X\% of improvement in ABC
    \item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}
 
\textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
Company Name \hfill \textit{San Francisco, CA}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved X\% growth for XYZ using A, B, and C skills.
     \item Led XYZ which led to X\% of improvement in ABC
    \item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

    {\bf Master of Computer Science}, Stanford University \hfill {Expected 2020}\\
    Relevant Coursework: A, B, C, and D.
    
    {\bf Bachelor of Computer Science}, Stanford University \hfill {2014 - 2017}
    %Minor in Linguistics \smallskip \\
    %Member of Eta Kappa Nu \\
    %Member of Upsilon Pi Epsilon \\

\end{rSection}

\end{document}
